%%% The main file. It contains definitions of basic parameters and includes all other parts.

%% Settings for single-side (simplex) printing
% Margins: left 40mm, right 25mm, top and bottom 25mm
% (but beware, LaTeX adds 1in implicitly)
\documentclass[12pt,a4paper]{report}
\setlength\textwidth{145mm}
\setlength\textheight{247mm}
\setlength\oddsidemargin{15mm}
\setlength\evensidemargin{15mm}
\setlength\topmargin{0mm}
\setlength\headsep{0mm}
\setlength\headheight{0mm}
% \openright makes the following text appear on a right-hand page
\let\openright=\clearpage


%% Settings for two-sided (duplex) printing
% \documentclass[12pt,a4paper,twoside,openright]{report}
% \setlength\textwidth{145mm}
% \setlength\textheight{247mm}
% \setlength\oddsidemargin{14.2mm}
% \setlength\evensidemargin{0mm}
% \setlength\topmargin{0mm}
% \setlength\headsep{0mm}
% \setlength\headheight{0mm}
% \let\openright=\cleardoublepage

%% Generate PDF/A-2u
\usepackage[a-2u]{pdfx}

%% Character encoding: usually latin2, cp1250 or utf8:
\usepackage[utf8]{inputenc}

%% Prefer Latin Modern fonts
\usepackage{lmodern}

%% Further useful packages (included in most LaTeX distributions)
\usepackage{amsmath}        % extensions for typesetting of math
\usepackage{amsfonts}       % math fonts
\usepackage{amsthm}         % theorems, definitions, etc.
\usepackage{bbding}         % various symbols (squares, asterisks, scissors, ...)
\usepackage{bm}             % boldface symbols (\bm)
\usepackage{graphicx}       % embedding of pictures
\usepackage{fancyvrb}       % improved verbatim environment
\usepackage{natbib}         % citation style AUTHOR (YEAR), or AUTHOR [NUMBER]
\usepackage[nottoc]{tocbibind} % makes sure that bibliography and the lists
			    % of figures/tables are included in the table
			    % of contents
\usepackage{dcolumn}        % improved alignment of table columns
\usepackage{booktabs}       % improved horizontal lines in tables
\usepackage{paralist}       % improved enumerate and itemize
\usepackage{xcolor}         % typesetting in color
\usepackage{subcaption}
\usepackage[ruled]{algorithm2e}
\usepackage[acronym,toc,shortcuts,nonumberlist]{glossaries}
\usepackage{diagbox}


\usepackage{color}
\definecolor{bluekeywords}{rgb}{0.13,0.13,1}
\definecolor{greencomments}{rgb}{0,0.5,0}
\definecolor{redstrings}{rgb}{0.9,0,0}

\usepackage{listings}
\lstset{language=[Sharp]C,
  showspaces=false,
  showtabs=false,
  breaklines=true,
  showstringspaces=false,
  breakatwhitespace=true,
  escapeinside={(*@}{@*)},
  commentstyle=\color{greencomments},
  keywordstyle=\color{bluekeywords},
  stringstyle=\color{redstrings},
  basicstyle=\ttfamily
}

\newacronym{AI}{AI}{Artificial Intelligence}
\newacronym{XR}{XR}{extended reality}
\newacronym{RTS}{RTS}{real-time strategy}
\newacronym{MCTS}{MCTS}{Monte-Carlo tree search}
\newacronym{Csharp}{C\#}{C Sharp}
\newacronym{OOP}{OOP}{Object Oriented Programming}

\makeglossaries


%%% Basic information on the thesis

% Thesis title in English (exactly as in the formal assignment)
\def\ThesisTitle{Artificial Intelligence for Quoridor game}

% Author of the thesis
\def\ThesisAuthor{Devyanshu Koirala}

% Year when the thesis is submitted
\def\YearSubmitted{2024}

% Name of the department or institute, where the work was officially assigned
% (according to the Organizational Structure of MFF UK in English,
% or a full name of a department outside MFF)
\def\Department{Department of Software and Computer Science Education (KSVI)}

% Is it a department (katedra), or an institute (ústav)?
\def\DeptType{Department}

% Thesis supervisor: name, surname and titles
\def\Supervisor{Mgr. Klára Pešková, Ph.D.}

% Supervisor's department (again according to Organizational structure of MFF)
\def\SupervisorsDepartment{KSVI}

% Study programme and specialization
\def\StudyProgramme{Computer Science}
\def\StudyBranch{Artificial Intelligence (AI)}

% An optional dedication: you can thank whomever you wish (your supervisor,
% consultant, a person who lent the software, etc.)
\def\Dedication{%
I would like to express my deepest gratitude to my supervisor, Mgr. Klára Pešková, Ph.D for her invaluable guidance and support. Her mentorship, expertise, dedication and constructive feedbacks have been vital throughout this journey.

Furthermore the constant support and encouragement from my friends and family have been my guiding light. To my family for always believing in my potential and for motivating me throughout my academic journey, my friends and my brother, who have played countless games of Quoridor with me in order to help me understand the game on a deeper level, I will forever be grateful.
}

% Abstract (recommended length around 80-200 words; this is not a copy of your thesis assignment!)
\def\Abstract{%
Quoridor presents a challenging terrain for strategic decision-making, making it a suitable testing ground for various Artificial Intelligence (AI) algorithms. This thesis explores the implementation of generic interfaces for AI agents and finally evaluation the AI agents in the game, namely Minimax, Monte Carlo Tree Search (MCTS) and A-star within the realm of Quoridor gameplay. In the thesis, we develop the AI interface that can be easily integrated into any other game. 

The research begins with a comprehensive overview of the Quoridor game, its rules and strategies. Subsequently, we delve into the theoretical foundations and practical implementation details of the aforementioned AI algorithms and conduct a thorough evaluation in an effort to determine the best one in this context.
}

% 3 to 5 keywords (recommended), each enclosed in curly braces
\def\Keywords{%
{Quoridor} {Artificial Intelligence} {AI} {Board Game}
}

%% The hyperref package for clickable links in PDF and also for storing
%% metadata to PDF (including the table of contents).
%% Most settings are pre-set by the pdfx package.
\hypersetup{unicode}
\hypersetup{breaklinks=true}

% Definitions of macros (see description inside)


% Title page and various mandatory informational pages
\begin{document}
\include{title}

%%% A page with automatically generated table of contents of the bachelor thesis

\tableofcontents

%%% Each chapter is kept in a separate file
\include{preface}
\include{chapters/game_description}
\include{chapters/related_works}
\include{chapters/game_analysis}
\include{chapters/background}
\include{chapters/implementation}
\include{chapters/experiments}
\include{epilog}

%%% Bibliography
\include{bibliography}

%%% Figures used in the thesis (consider if this is needed)
%\listoffigures

%%% Tables used in the thesis (consider if this is needed)
%%% In mathematical theses, it could be better to move the list of tables to the beginning of the thesis.
%\listoftables

%%% Abbreviations used in the thesis, if any, including their explanation
%%% In mathematical theses, it could be better to move the list of abbreviations to the beginning of the thesis.
\printglossaries


%%% Attachments to the bachelor thesis, if any. Each attachment must be
%%% referred to at least once from the text of the thesis. Attachments
%%% are numbered.
%%%
%%% The printed version should preferably contain attachments, which can be
%%% read (additional tables and charts, supplementary text, examples of
%%% program output, etc.). The electronic version is more suited for attachments
%%% which will likely be used in an electronic form rather than read (program
%%% source code, data files, interactive charts, etc.). Electronic attachments
%%% should be uploaded to SIS and optionally also included in the thesis on a~CD/DVD.
%%% Allowed file formats are specified in provision of the rector no. 72/2017.
\appendix
\chapter{Attachments}

\section{Repository}
\label{app:repository}
The implementation can be found here:  \url{https://github.com/devyanshuk/Quoridor}

\section{User Documentation}

\subsection{Console Application}
\label{app:consoleapp}
The Console application user documentation can be found in \textbf{Docs/ConsoleUserDoc.md}.

\subsection{Desktop Application}
\label{app:desktopapp}
The Desktop application user documentation can be found in \textbf{Docs/DesktopUserDoc.md}.

\section{Programmer Documentation}
\label{app:programmerdoc}
The programmer documentation can be found in \textbf{Docs/ProgrammerDoc.md}.

\section{Scripts}
\label{app:scripts}
All scripts used in the experiments can be found in \textbf{Scripts/} directory.

\openright
\end{document}
